### 2020-04-15 dataclean.tex
figure placement

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Viewing and Cleaning the Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Viewing and Cleaning the Data}
\label{section:dataclean}
As we need to recover durations in operation from this data, correct
processing involves time adjustments for switching between daylight
saving time and standard time and leap years. We perform this by
setting a reference time zone (Eastern time) and converting all
date-times from strings into POSIX date-time variables with the R
\pkg{lubridate} package \cite{lubridate}, which enables appropriate
date arithmetic and sensible date constructs for graphs.

@@

To get some intuition for the GPU lifetimes on Titan, we give two
views of 80 randomly selected GPUs (Figure~\ref{fig:gpuview}) and 80
randomly selected locations (Figure~\ref{fig:locview}). The GPU view
visually documents the life of the unit: when it was installed and
removed at various locations, its DBE and OTB events, and the last
time it was seen. The location view documents the life of a location:
when different GPUs were installed and removed, their OTB and DBE
events, and whether a removal was the last time the unit was seen on
the system. These views were critical to understanding the data and to
verifying various processing decisions.
\begin{figure*}[tb]
  \includegraphics[width=6.5in]{figs/sample_sn.pdf}
  \caption{GPU serial number view of life and failures. Legend: black
    dots are installs, black lines are lifetimes at installed
    location, blue squares are OTB events, red triangles are DBE
    events, and black ] are ``last seen'' events.}
  \label{fig:gpuview}
\end{figure*}
\begin{figure*}[tb]
  \includegraphics[width=6.5in]{figs/sample_loc.pdf}
  \caption{GPU location view of life and failures.  Legend: black
    dots are installs, black lines are lifetimes at installed
    location, blue squares are OTB events, red triangles are DBE
    events, and black ] are ``last seen'' events.}
  \label{fig:locview}
\end{figure*}

The third rework cycle was used to label GPUs as old batch and new
batch. The two batches are clearly identifiable in the GPU view. Also,
more frequent OTB and DBE events are apparent in the old batch. It is
also clear from this view that most new GPUs stay at the initial
install location whereas the old GPUs were occasionally reinstalled at
new locations. Nevertheless, a separate analysis determined that the
vast majority of time of the vast majority of units is spent at one
location by both the new and the old units.

>>>>

% !TEX root = main.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Viewing and Cleaning the Data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Viewing and Cleaning the Data}
\label{section:dataclean}
\begin{figure*}[bt]
  \includegraphics[width=6.5in]{figs/sample_sn.pdf}
  \caption{GPU serial number view of life and failures. Legend: black
    dots are installs, black lines are lifetimes at installed
    location, blue squares are OTB events, red triangles are DBE
    events, and black ] are ``last seen'' events.}
  \label{fig:gpuview}
\end{figure*}
As we need to recover durations in operation from this data, correct
processing involves time adjustments for switching between daylight
saving time and standard time and leap years. We perform this by
setting a reference time zone (Eastern time) and converting all
date-times from strings into POSIX date-time variables with the R
\pkg{lubridate} package \cite{lubridate}, which enables appropriate
date arithmetic and sensible date constructs for graphs.

@@

To get some intuition for the GPU lifetimes on Titan, we give two
views of 80 randomly selected GPUs (Figure~\ref{fig:gpuview}) and 80
randomly selected locations (Figure~\ref{fig:locview}).
\begin{figure*}[tb]
  \includegraphics[width=6.5in]{figs/sample_loc.pdf}
  \caption{GPU location view of life and failures.  Legend: black
    dots are installs, black lines are lifetimes at installed
    location, blue squares are OTB events, red triangles are DBE
    events, and black ] are ``last seen'' events.}
  \label{fig:locview}
\end{figure*}
The GPU view
visually documents the life of the unit: when it was installed and
removed at various locations, its DBE and OTB events, and the last
time it was seen. The location view documents the life of a location:
when different GPUs were installed and removed, their OTB and DBE
events, and whether a removal was the last time the unit was seen on
the system. These views were critical to understanding the data and to
verifying various data processing decisions.

The third rework cycle was used to label GPUs as old batch and new
batch. The two batches are clearly identifiable in the GPU view. More
frequent OTB and DBE events are apparent in the old batch. It is also
clear from this view that practically all new GPUs stayed at their
initial install location whereas the old GPUs were occasionally
reinstalled at new locations. Nevertheless, a separate analysis
determined that the vast majority of time of the vast majority of
units is spent at one location by both the new and the old units.
